E1: ENRON Sentiment

### 2016-03-24 paper/paper.tex
started RW
doing RW

\section{Related work}
\label{sec:r-w}
TODO

>>>>

\section{Related work}
\label{sec:r-w}

\subsection{Email Dataset Analysis}
About email dataset analysis, literature reports many works focused on exploring, filtering and describing email datasets.
Datasets can be noisy and some preparatory work like filtering and reorganising might be helpful to have a better grip on the data.
For instance,~\cite{klimt2004introducing} provides metrics of the ``ENRON corpus'' as well as a description of it structure.
A thorough analysis of such structure highlights the presence of redundant and SPAM messages.
Similarly,~\cite{zhou2007strategies} describes some cleaning strategies for the aforementioned corpus.
In particular, the authors analyse the actual difficulties in cleaning a corporate email dataset which in the ENRON case are multiple and mainly related to the text-parsing phase.
Indeed, the authors claim there are a certain amount of duplicate emails, addresses and attachments which might come in a slightly different format, making the parsing more challenging.

\subsection{Sentiment Extraction}
TODO

\subsection{Large-scale Data Processing Tools}
TODO
